### 2016-07-06 motivation.tex
edits

We have thus far assumed a strongly consistent ({\sc sc}) store that,
in the absence of transactions with special isolation requirements,
makes the effects of any operation immediately visible to all
subsequent operations. The natural behaviour of {\sc sc} to totally
order all operations w.r.t. the $\hbZ$ relation could be in conflict
with the constraints imposed by weak isolation. To meet the
requirements of weaker isolation levels, say {\sc rc}, the store has
to adapt itself to \emph{hide} the effects of concurrent transactions
until they are committed. Once committed though, effects need to be
immediately visible to subsequent operations. This semantics can be
built into the reasoning framework, leading to a proof system
tailor-made for such stores. However, for the reasoning framework to
be truly useful, it has to be parametric over different consistency
semantics, supporting stores that are weaker than {\sc sc} (e.g.,
causally or eventually consistent), and should be able to reconcile
conflicts between consistency and isolation constraints.  We
demonstrate how our reasoning framework makes this possible in the
following sections.

>>>>

Implicit in the above discussion is the assumption of a strongly
consistent ({\sc sc}) store that guarantees the visibility of all
previously committed transactions. An {\sc sc} semantics can be built
into the reasoning framework, leading to a proof system tailor-made
for such stores.  However, for the reasoning framework to be truly
useful, it should be capable of handling different consistency
semantics, supporting stores that are weaker than {\sc sc} (e.g.,
causally or eventually consistent), and should be able to reconcile
conflicts between consistency and isolation constraints.  We
demonstrate how our reasoning framework makes this possible in the
following sections.

%% We have thus far assumed a strongly consistent ({\sc sc}) store that,
%% in the absence of transactions with special isolation requirements,
%% makes the effects of any operation immediately visible to all
%% subsequent operations. The natural behaviour of {\sc sc} to totally
%% order all operations w.r.t. the $\hbZ$ relation could be in conflict
%% with the constraints imposed by weak isolation. To meet the
%% requirements of weaker isolation levels, say {\sc rc}, the store has
%% to adapt itself to \emph{hide} the effects of concurrent transactions
%% until they are committed. Once committed though, effects need to be
%% immediately visible to subsequent operations. This semantics can be
%% built into the reasoning framework, leading to a proof system
%% tailor-made for such stores. However, for the reasoning framework to
%% be truly useful, it has to be parametric over different consistency
%% semantics, supporting stores that are weaker than {\sc sc} (e.g.,
%% causally or eventually consistent), and should be able to reconcile
%% conflicts between consistency and isolation constraints.  We
%% demonstrate how our reasoning framework makes this possible in the
%% following sections.

### 2016-07-06 store-consistency.tex
edits

  \item The value written to \C{B} is either $\C{k-a1-a2}$ or
  $\C{k-a1}$ depending on whether or not \C{Wd1} has already
  committed. This is clearly necessary to deduce the value of \C{B}
  before and after \C{Wd1} commits.
\end{itemize}
The resultant rely relation ($R_1$) is shown below (note: we
write $(\E'-\E) \Vdash {\committed(\C{Wd2})}$ to express that \C{Wd2}
is not committed in $\E$, but committed in $\E'$.):
\vspace*{-1.5pt}
\begin{smathpar}
\begin{array}{lcl}
  R_1 & = & \{ (\E,\E') \;|\; \neg\underE{\committed(\C{Wd1})} \conj
        (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
%       \neg\underE{\committed(\C{Wd2})} \conj \I(\E) \conj \I(\E')\\
%       \conj (\E'-\E) \subseteq \C{Wd2} \conj \\
%   & & \hspace*{0.5in} \E' \Vdash \committed(\C{Wd2}) ~\Rightarrow~ \E'
%       \Vdash \C{Wd2} \wrstoar \C{B} \conj \\ 
%   & & \hspace*{0.5in} \underE{\committed(\C{Wd1})} \conj \E' \Vdash
%   \committed(\C{Wd2}) \Rightarrow \C{B=k-a1-a2} \\
%   & & \hspace*{0.5in} \neg\underE{\committed(\C{Wd1})} \conj
%       (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
    & & \hspace*{0.8in}\Rightarrow \C{B=k-a2} \conj 
        \E' \Vdash \C{Wd2} \wrstoar \C{B} \\
    & & \hspace*{0.37in} \conj \underE{\committed(\C{Wd1})} \conj
        (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
%       \C{COMMIT(Wd2)} \in (\E'.\A-\E.\A) \\
    & & \hspace*{0.6in}\Rightarrow \C{B=k-a1-a2} \conj
        \E' \Vdash \C{Wd2} \wrstoar \C{B} \\
    & & \hspace*{0.37in}\conj \forall(\eta \in \E'.\A - 
        \E.\A).~\txn(\eta) = \C{Wd2}\}\\
\end{array}
\end{smathpar}

>>>>

  \item The value written to \C{B} is either $\C{k-a1-a2}$ or
  $\C{k-a1}$ depending on whether or not \C{Wd1} has already
  committed. This is clearly necessary to deduce the value of \C{B}
  before and after \C{Wd1} commits.
\end{itemize}
The resultant rely relation ($R_1$) is shown below\footnote{We
  write $(\E'-\E) \Vdash {\committed(\C{Wd2})}$ to express the property
  that \C{Wd2} is not committed in $\E$, but committed in $\E'$.}:

\begin{smathpar}
\begin{array}{lcl}
  R_1 & = & \{ (\E,\E') \;|\; \neg\underE{\committed(\C{Wd1})} \conj
        (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
%       \neg\underE{\committed(\C{Wd2})} \conj \I(\E) \conj \I(\E')\\
%       \conj (\E'-\E) \subseteq \C{Wd2} \conj \\
%   & & \hspace*{0.5in} \E' \Vdash \committed(\C{Wd2}) ~\Rightarrow~ \E'
%       \Vdash \C{Wd2} \wrstoar \C{B} \conj \\ 
%   & & \hspace*{0.5in} \underE{\committed(\C{Wd1})} \conj \E' \Vdash
%   \committed(\C{Wd2}) \Rightarrow \C{B=k-a1-a2} \\
%   & & \hspace*{0.5in} \neg\underE{\committed(\C{Wd1})} \conj
%       (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
    & & \hspace*{0.8in}\Rightarrow \C{B=k-a2} \conj 
        \E' \Vdash \C{Wd2} \wrstoar \C{B} \\
    & & \hspace*{0.37in} \conj \underE{\committed(\C{Wd1})} \conj
        (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
%       \C{COMMIT(Wd2)} \in (\E'.\A-\E.\A) \\
    & & \hspace*{0.6in}\Rightarrow \C{B=k-a1-a2} \conj
        \E' \Vdash \C{Wd2} \wrstoar \C{B} \\
    & & \hspace*{0.37in}\conj \forall(\eta \in \E'.\A - 
        \E.\A).~\txn(\eta) = \C{Wd2}\}\\
\end{array}
\end{smathpar}
